---
title: "MAHINDRA  SENTIMENT ANALYSIS"
author: "RITWIKA BHATTACHARJEE"
date: "06/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r}
CarSales <- read.csv("C:/Users/hp/Desktop/FALL-2020-21/Mahindra Project/Datasets/CarSales.csv", header=TRUE)
```

```{r}
head(CarSales)
```

## <b> POSITIVE SENTIMENT ANALYSIS </b>

### <b> CARS IN PRICE RANGE 5-10 </b>

```{r}
cars0to5 = CarSales %>%
  filter(Price.Category == '5-10')
#remove NA values

cars0to5 = cars0to5[complete.cases(cars0to5),]
```

#### Analysis by Manufacturer or OEM
```{r}
#Average sales of each manufacturer
cars0to5 %>%
  group_by(OEM) %>%
  summarise(avg_sales_2018 = mean(FY18), avg_sales_2019 = mean(FY19), total_avg_sales = (mean(FY18)+mean(FY19))/2) %>%
  dplyr::select(OEM, avg_sales_2018, avg_sales_2019, total_avg_sales) %>%
  arrange(desc(total_avg_sales))
```

### <b>Observation: </b> It is observed that top 5 manufacturers corresponding to maximum sales in both years is Maruti Suzuki, Hyundai, Honda, Tata, Mahindra

#### Analysis by car manufacturer and car category

```{r}
#Average sales of each manufacturer and car category
cars0to5 %>%
  group_by(OEM, Car.Category) %>%
  summarise(avg_sales_2018 = mean(FY18), avg_sales_2019 = mean(FY19), total_avg_sales = (mean(FY18)+mean(FY19))/2) %>%
  dplyr::select(OEM, Car.Category, avg_sales_2018, avg_sales_2019, total_avg_sales) %>%
  arrange(desc(total_avg_sales))
```

### <b> Observation </b> The top ten cars having highest average sales are:
####1. Maruti Suzuki	Compact sedanÿ
####2. Maruti Suzuki	Super Mini
####3. Maruti Suzuki	Hatch
####4. Hyundai	Supermini
####5. Maruti Suzuki	Hatback
####6. Hyundai	Hatch
####7. Mahindra	SUV
####8. Honda	Compact Sedan
####9. Tata	SUV
####10. Hyundai	compact SUV

#### To analyse the sentiment of customers we have to find the prominent features in these car categories which primary attracted the customers

```{r}
CarFeatures <- read.csv("C:/Users/hp/Desktop/FALL-2020-21/Mahindra Project/Datasets/CarFeatures.csv", header=TRUE)
```

```{r}
CarFeatures = CarFeatures %>%
  filter(Price.Band..Lakh == "fiveten")
dim(CarFeatures)
```

#### Displaying the list of features in each of these cars
```{r}
x = CarFeatures %>%
  filter(OEM == "Maruti Suzuki", Car.Category == "Compact sedanÿ") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = colnames(x)
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Maruti Suzuki", Car.Category == "Super Mini") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[1,]
x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Maruti Suzuki", Car.Category == "Hatch") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Hyundai", Car.Category == "Supermini") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Maruti Suzuki", Car.Category == "Hatback") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Hyundai", Car.Category == "Hatch") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Mahindra", Car.Category == "SUV") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Honda", Car.Category == "Compact Sedan") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Tata", Car.Category == "SUV") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
x = CarFeatures %>%
  filter(OEM == "Hyundai", Car.Category == " compact SUV") %>%
  dplyr::select(-Price.Band..Lakh, -OEM, -MODEL,-Car.Category, -LATEST.LAUNCH.1EAR.20..., -VARIANT, -COST.Ex.Showroom.)

x = x[ , colSums(is.na(x)) == 0]

features_list = append(features_list, colnames(x))
```

```{r}
#finding frequencies of each features in the top sold cars
freqdata = as.data.frame(table(features_list))
freqdata = freqdata %>%
  arrange(desc(Freq))
head(freqdata,30)
```

### <b> Observation </b> According to customers positive sentiment analysis these are the top 30 desirable features in cars of price range 5 to 10 lacs 

#### Further we can also group the above features into types of features to understand which category of features is most valued by customers

```{r}
freqdata = freqdata %>%
  mutate(features_list = gsub('\\.',"",features_list))

FeatureDesc <- read.csv("C:/Users/hp/Desktop/FALL-2020-21/Mahindra Project/Datasets/FeatureDesc.csv")

FeatureDesc = FeatureDesc %>%
  mutate(Feature = gsub("[[:punct:]]", "", Feature)) %>%
  mutate(Feature = gsub(" ","",Feature))

```

```{r}
FeatureDesc$Feature.Category = as.character(FeatureDesc$Feature.Category)
library(stringr)
FeatureDesc$shortcat <- substr(word(FeatureDesc$Feature.Category, 1),1,8)

catlist=c()
for (i in seq(1,dim(freqdata)[1])){
  catlist = append(catlist, FeatureDesc$shortcat[FeatureDesc$Feature==as.character(freqdata$features_list[i])])
}
table(catlist)
barplot(table(catlist))
```

### <b>Observation: It can be observed from the above analysis that customers of cars in price range 5 to 10 lacs prefer Comfort, safety and exterior car features over entertainment and interior features </b>


